Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-11-03 paper.tex
Revise IOTA descriptions

To address the inefficiency of the Blockchain, \textbf{IOTA}\cite{IOTAwhitepaper} is a cryptocurrency for the IoT industry based on a revolutionary distributed ledger technology, the \textbf{Tangle}, which enables zero-transaction. On top of that, \textbf{Masked Authenticated Messaging(MAM)}\cite{MAM}, is provided for a second layer data communication protocol which allows transmission, access, and verification of an encrypted data stream over the Tangle where privacy and integrity meet.

>>>>

To address the inefficiency of the Blockchain, \textbf{IOTA}\cite{IOTAwhitepaper} is a cryptocurrency for the IoT industry based on a revolutionary distributed ledger technology, the \textbf{Tangle}, which creates the potential for feeless transactions between users and statistically indefinite network scalability. On top of that, \textbf{Masked Authenticated Messaging(MAM)}\cite{MAM}, is provided for a second layer data communication protocol which allows transmission, access, and verification of an encrypted data stream over the Tangle where privacy and integrity meet.
